Visualizations for the manuscript

### 2022-03-23 metanalysis_visualization/manuscript_Figures.Rmd
forest plot: reordering and changing square sizes proportions

metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall periods' slope differences")
```

@@

forest(model_meta_country, 
       slab = trends_country$country,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```

>>>>

metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                plim = c(1, NA),
                order = "obs",
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
```

@@

forest(model_meta_country, 
       slab = trends_country$country,
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```
